CSCI 598A - Project Proposal

### 2014-03-03 proposal/proposal.tex
Added a few notes. Also, my first LaTeX edit!
LaTeX fun

\title{CSCI-598a Project Proposal}
\author{Kevin Emery, Santiago Gonzalez, Brandon Rodriguez, Taylor Sallee}
\date{March 17, 2014}

@@

@@

\section{Summary}
A summary

\section{References}
References with \textbf{BibTeX}

>>>>

\title{CSCI 598A - Project Proposal}
\author{Kevin Emery, Santiago Gonzalez, Brandon Rodriguez, Taylor Sallee\\ \emph{Undergraduates, EECS Department, Colorado School of Mines}}
\date{March 17, 2014}
ga

@@

\begin{abstract}
300 words or less. Also, we need to put the EECS department in the title area as our professional affiliation.
\end{abstract}

@@

\section{Summary}
A summary \cite{someone2013}

\begin{thebibliography}{99}
\bibitem{someone2013} Somebody
\bibitem{johnson2012} X. Johnson
\end{thebibliography}
